---
title: "Upload instructions and tips"
author: "FES611a"
date: "12/5/2019"
output: html_document
---

Hello,

Here's an outline for the final presentation where everyone's work takes up one slide.
There are multiple ways to do this:
  1) embed the code and run it through the R each time
  2) do all the preprocessing on your personal computer -> save final plots as an image -> upload the image onto a common directory (say on Canvas)
  3) repeat steps in (2) but before you upload the plot, make a poster of it (in powerpoint, inkscape, etc) and then upload that poster (as an image) onto the directory
  
Method 1) is going to be hardest to put together, because it'll take a lot of time to run the code and we'll need all the datafiles (kindly email [Akshay](akshay.surendra@yale.edu) who'll put it together)
Method 2) is ideal if you don't need too much text around your final plot - if your plot labels, title etc. are sufficiently informative
Method 3) is ideal if you need to add some description around your final plot

#Saving your figures in R

 - By default, powerpoint uses a 13.3 inch x 7.5 inch screen size, so it'll be great if all your figures are formatted to fit this 
 - if you're using `base-R`, you could save plots this way -
```{r,include=TRUE,message=FALSE,warning=FALSE,echo=TRUE}
#all your code goes up here
data("mtcars")
dat<-data.frame(x = scale(mtcars$mpg),y = scale(mtcars$hp))

png(
  file="./correctpath/EDSoutput_trial.png",
  width=6, height=4, units="in",
  res=300) # this creates an empty .png file with these specification of width, height in inches and with a resolution of 300 pixels/square-inch

plot(x = dat$x,y = dat$y) #this is the plot that fills the file

dev.off() #this tells R to stop filling the .png
```
 - There are lots of resources online to figure out what works best, like this [link]('https://www.datamentor.io/r-programming/saving-plot/').

 - Alternatively, you could use `ggsave()` for a `ggplot` object:
```{r}
library(ggplot2)
data("diamonds")
fig1<-ggplot(data = diamonds) + geom_point(aes(y=carat,x=price)) + theme_bw() #store your figure in an object

ggsave(filename = "./correctpath/EDoutput_trial.png",
       plot = fig1,device = "png",
       width = 5,height = 6,units = "in",dpi = 300) #saves the object to a file with a specific format, size and resolution (dpi)
```

 - if you have multiple plots, you can use par(mfrow = c(rows,columns)) in base-R or use grid.arrange(c(plot1,plot2,...plotn),nrow = rows, ncol = columns) from the gridExtra package
 - Some resources to do this in [](base-R)
 - Some resources to do this with ggplot objects with [](`gridExtra`) and [](`cowPlot`)
 - Once you save the plot, you can read images into the .Rpres file (example shown in the .Rpres file)
 - If you use Python, you an ignore this document and directly upload the figure onto the .Rpres file (through R though)